%-------------------------
% Resume in Latex
% Author: Guna Palanivel
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Guna Palanivel} \\ \vspace{1pt}
    Chennai, 600 089, India \\ \vspace{1pt}
     \href{tel:+919952380651}{\raisebox{-0.2\height}\faPhone\ \underline{+91 9952380651}} ~
    \href{mailto:gunapalanivel2003@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{gunapalanivel2003@gmail.com}} \\
    \vspace{8pt} % Additional space between rows
    \href{https://www.linkedin.com/in/guna-palanivel/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/guna-palanivel}}  ~
    \href{https://github.com/GunaPalanivel}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/GunaPalanivel}} ~
    \href{https://gunaprofile.pages.dev}{\raisebox{-0.2\height}\faGlobe\ \underline{gunaprofile.pages.dev}}
    \vspace{-8pt}
\end{center}





%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM University}{Sep 2021 -- Jun 2025}
      {BTech In Electronics and Communication Engineering}{Chennai, India}

      \resumeSubheading
      {SRI Ragavendra School}{Mar 2020 -- May 2021}
      {Higher Secondary Course in Computer Science and Mathematics}{Salem, India}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[left=0pt, itemsep=-2pt]
    \item \textbf{Programming Languages:} HTML5, CSS3, JavaScript (ES6+)
    \item \textbf{Database:} MySQL, MongoDB
    \item \textbf{Operating System:} Windows Subsystem for Linux (WSL), Ubuntu (WSL)
    \item \textbf{Version Control:} Git, GitHub
    \item \textbf{Software:} Visual Studio Code, MySQL Workbench, Anaconda Navigator
\end{itemize}
\vspace{-16pt}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IOTIOT.in}{Dec 2023 -- Present}
      {UI Designer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Currently leading efforts to understand and meticulously document the existing router UI code, addressing long-standing challenges arising from outdated and undocumented code. Employing a comprehensive strategy, including mapping page structures, elucidating folder and file hierarchies, and dissecting HTML, JS, and CSS intricacies.}
        \resumeItem{Ensured that the documentation adheres to industry-standard markdown formats, providing a clear and comprehensive reference for future modifications. }
        \resumeItem{Collaborated with a team of two members, guided by a team lead, to design a user-friendly UI for Industrial Routers in Figma. Showcased effective teamwork, merging diverse skills to create an innovative design aligned with project goals and user needs.}
        \resumeItem{Successfully optimized UI design within the constraints of routers with less than 8MB of storage space, prioritizing efficiency in configuration processes while minimizing disk space and RAM usage.}
      \resumeItemListEnd


    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------COURSES AND TRAINING-----------

\section{Courses and Training}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FULL STACK WEB DEVELOPER - MEAN STACK}{May 2023 -- Present}
      {simplilearn.com}{Master's Program}
      \resumeItemListStart
        \resumeItem{Currently pursuing an advanced Master's Program in Full Stack Web Development with a focus on the MEAN stack, demonstrating a commitment to staying at the forefront of industry advancements.}
        \resumeItem{Gaining in-depth expertise in HTML5, CSS3, JavaScript, My SQL, and MongoDB through rigorous coursework and hands-on projects, ensuring proficiency across the entire web development stack.}
        \resumeItem{Applying theoretical knowledge to real-world scenarios, actively engaging in practical projects within the Master's Program to develop tangible skills in designing and implementing MEAN stack solutions.}
        \resumeItem{Demonstrated a strong understanding of the Git version control system and utilized it effectively for collaborative development.}
      \resumeItemListEnd


    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
{\textbf{BANKIST} $|$ \emph{\href{https://github.com/GunaPalanivel/Bankist.git}{Github} | \href{https://bankist-259ikqlgf-guna-palanivels-projects.vercel.app/}{Preview}}}{HTML, CSS, JS}
          \resumeItemListStart
            \resumeItem{Spearheaded the development of the Bankist App, a dynamic online banking application, focusing on DOM manipulation and event-handling techniques using HTML, CSS, and JavaScript. This project was originally introduced by Jonas Schmedtmann.}
            \resumeItem{  Enhanced the user experience by incorporating various functionalities such as checking account balances, transferring money between accounts, requesting loans, and closing accounts seamlessly within the application.}
            \resumeItem{Applied modern JavaScript features, such as asynchronous programming, advanced array manipulation, and data handling techniques, to enhance the functionality and user experience of the banking application.}
            \resumeItem{Implemented robust account features, including secure user authentication, real-time transaction management, and dynamic UI updates.}

          \resumeItemListEnd
          \vspace{-13pt}

    \resumeSubHeadingListEnd
\vspace{-15pt}


%

\end{document}